Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2024-04-03 latex/figure5.tex
Simplify code boxes
Rename shaded code environments
Rename load_model to load in biomodels

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{from}\ClassTok{ simbio.io }\KeywordTok{import}\ClassTok{ biomodels, sbml}

\VariableTok{model }\OperatorTok{=}\ClassTok{ sbml}.\FunctionTok{load}\KeywordTok{(}\StringTok{"repressilator.sbml"}\KeywordTok{)}  \CommentTok{\# from existing SBML file}
\VariableTok{model }\OperatorTok{=}\ClassTok{ biomodels}.\FunctionTok{load\_model}\KeywordTok{(}\StringTok{"BIOMD12"}\KeywordTok{)}  \CommentTok{\# from BioModels}
\VariableTok{model}
\end{Highlighting}
\end{Shaded}

\begin{longtable}{@{}lll@{}}
    \multicolumn{3}{l}{Elowitz2000 - Repressilator} \\
    \toprule\noalign{}
    type & total & names \\
    \midrule\noalign{}
    \endhead
    \bottomrule\noalign{}
    \endlastfoot
    variables  &  6 & PX, PY, PZ, X, Y, Z \\
    parameters & 17 & cell, beta, alpha0, alpha, eff, n, KM, tau\_mRNA, tau\_prot, ... \\
    equations  & 12 & Reaction1, Reaction2, Reaction3, Reaction4, Reaction5, ... \\
\end{longtable}

>>>>

\begin{CodeInput}
\begin{Highlighting}[]
\KeywordTok{from}\ClassTok{ simbio.io }\KeywordTok{import}\ClassTok{ biomodels, sbml}

\VariableTok{model }\OperatorTok{=}\ClassTok{ sbml}.\FunctionTok{load}\KeywordTok{(}\StringTok{"repressilator.sbml"}\KeywordTok{)}  \CommentTok{\# from existing SBML file}
\VariableTok{model }\OperatorTok{=}\ClassTok{ biomodels}.\FunctionTok{load}\KeywordTok{(}\StringTok{"BIOMD12"}\KeywordTok{)}  \CommentTok{\# from BioModels}
\VariableTok{model}
\end{Highlighting}
\end{CodeInput}

\begin{CodeOutput}
    \begin{longtable}{@{}lll@{}}
        \multicolumn{3}{l}{Elowitz2000 - Repressilator} \\
        \toprule\noalign{}
        type & total & names \\
        \midrule\noalign{}
        \endhead
        \bottomrule\noalign{}
        \endlastfoot
        variables  &  6 & PX, PY, PZ, X, Y, Z \\
        parameters & 17 & cell, beta, alpha0, alpha, eff, n, KM, tau\_mRNA, tau\_prot, ... \\
        equations  & 12 & Reaction1, Reaction2, Reaction3, Reaction4, Reaction5, ... \\
    \end{longtable}
\end{CodeOutput}
